\documentclass{article}
\usepackage[letterpaper, total={7.5in, 10in}]{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\vspace{-12pt}\centering\rule{7.5in}{0.4pt}\vspace{-12pt}]

\pagenumbering{gobble}

% Custom Commands
\newcommand{\underlinedLink}[2]{
    {\underline{\large \href{#1}{#2}}}
}

\newcommand{\itemInTable}[1]{
    \begin{itemize}
        \list{#1}
    \end{itemize}
}

\newcommand{\tabitem}[2]{
    \begin{tabular}{lp{#1}}
        \textbullet & #2
    \end{tabular} \vspace{0pt}
}

\begin{document}

% Title section
\begin{spacing}{1.4}
    \begin{center}
        {\bf\Huge Arnav Revankar} \\
        {\large Junior Computer Engineer @ NJIT} \\
        \underlinedLink{https://github.com/avr34}{github.com/avr34} $|$ \underlinedLink{mailto:avr33@njit.edu}{avr33@njit.edu} $|$ \underlinedLink{https://linkedin.com/in/avr33}{linkedin.com/in/avr33}
    \end{center}
\end{spacing}
\vspace{-9pt}

% --------------------------SUMMARY--------------------------
%\section{Summary}
%    \begin{center}
%        \begin{tabular}{p{0.96\textwidth}}
%            Highly motivated Computer Engineering student with a strong passion for Embedded Systems. Seeking an internship/coop opportunity to apply my skills and gain experience with real world engineering. \\
%        \end{tabular}
%    \end{center}

\section{Education}
    \vspace{-5pt}\begin{center}
        \begin{tabular}{p{0.99\textwidth}}
            {\large \bf New Jersey Institute of Technology} (Sept 2023 - Present) \hfill Cumulative GPA: 3.65 \\
            BS Computer Engineering, Minor in Data Analytics \hfill Newark, NJ
        \end{tabular}
    \end{center}
    \vspace{-10pt}\begin{itemize}
        \item {\bf Coursework:} Circuits and Systems 1 \& 2, Microprocessors, Computer Architecture, Applied Machine Learning, Digital Design, and others.
        \item {\bf Activities:} IEEE-HKN Inductee, 2026 Hackathon Volunteer
    \end{itemize}

    \vspace{-15pt}\begin{center}
        \begin{tabular}{p{0.99\textwidth}}
            {\large \bf County College of Morris} (Sept 2022 - May 2023) \hfill Cumulative GPA: 3.83 \\
            Challenger Program for High School Students \hfill Randolph, NJ
        \end{tabular}
    \end{center}
    \vspace{-10pt}\begin{itemize}
        \item Completed over two semesters as a part-time student.
    \end{itemize}

\section{Experience} \vspace{4pt}
    \raggedright\begin{tabular}{lr}
        \parbox[l]{3.65in}{\bf{\large{Software Engineering Intern}}} &
        \parbox[r]{3.65in}{\raggedleft March 2025 - August 2025} \\
        \parbox[l]{3.65in}{\href{https://www.mathnasium.com/math-centers/chatham}{\underline{Mathnasium}}} &
        \parbox[r]{3.65in}{\raggedleft Chatham, NJ}
    \end{tabular}
    \vspace{-10pt}\begin{itemize} 
        \setlength{\itemsep}{-2pt}
        \item Spearheaded a project developing a full-stack Javascript/Node.js email generator for parents of students at a Mathnasium tutoring center.
        \item Effectively employs a BNF Grammar, that is used to generate syntactically valid text from a set of customizable templates.
        \item Currently being used to send 110-150 emails per day, saving 5 centers 30-40 hours a week.
    \end{itemize}
    
    % \raggedright\begin{tabular}{lr}
    %     \parbox[l]{3.65in}{\bf{\large{Undergraduate Research Assistant}}} &
    %     \parbox[r]{3.65in}{\raggedleft October 2025 - Present} \\
    %     \parbox[l]{3.65in}{Assisting \underline{\href{https://tao-han-njit.netlify.app/}{Prof. Tao Han}}} &
    %     \parbox[r]{3.65in}{\raggedleft Newark, NJ}
    % \end{tabular}
    % \vspace{-10pt}\begin{itemize} 
    %     \setlength{\itemsep}{-2pt}
    %     \item Assisting in the development of a Microsoft Hololens application, for CV-based object detection.
    % \end{itemize}

\section{Skills} \vspace{4pt}
    \begin{itemize}
        \setlength{\itemsep}{-2pt}
        \item {\bf Languages:} C, C++, MATLAB, Java, Python, Go, SQL (MySQL), GNU Octave, \LaTeX, Javascript, VHDL
        \item {\bf Software Tools:} Linux/Unix, KiCAD, FreeCAD, STM32CubeMX \& IDE, PlatformIO, ESP-IDF, Git, Docker, Excel
        \item {\bf Build Tools/Debuggers:} Apache Maven, Apache Ant, CMake, Make, MSVC \& GCC, GDB, Valgrind
	    \item {\bf Libraries:} STM32 HAL, FreeRTOS, NumPy, PyTorch, Scikit Learn, Matplotlib, Gnuplot
        \item {\bf Communication Protocols:} UART, I2C, SPI, CAN, USB 2.0, TCP and Socket programming in C/C++ and Go
    \end{itemize}

\section{Projects}
    \raggedright\begin{tabular}{lr}
        \parbox[l]{3.65in}{{\bf{\large{SolarVision Autonomous Mower}}} \href{https://github.com/SolarVisionMower/SolarVision}{(\underline{Github})}} &
        \parbox[r]{3.65in}{\raggedleft Sept 2025 - Present} \\
    \end{tabular}
    \begin{itemize} \vspace{-5pt}
        \setlength{\itemsep}{-2pt}
        \item YOLO and LiDAR-based autonomous lawnmower, engineering capstone project. Still in progress
        \item Designed a \href{https://github.com/SolarVisionMower/SolarVision/blob/dev/PCBDesign/Hardware/STM32N6_Board/schematic.pdf}{\underline{custom 6-layer PCB}} for STM32N6 MCU, with external SPI NOR Flash and SDRAM Memory through the FMC.
        \item Trained a YOLOv8 Segmentation model on a custom dataset, and exported to C for the STM32N6 NPU, with the ST Edge AI Tool Suite.
        \item Currently working on interfacing integrating all sub-systems.
    \end{itemize}

    \raggedright\begin{tabular}{lr}
        \parbox[l]{3.65in}{{\bf{\large{8-Channel Logic Analyzer}}} \href{https://github.com/ragusauce4357/ECE692-Final-Project}{(\underline{Github})}} &
        \parbox[r]{3.65in}{\raggedleft Feb 2026 - Present} \\
    \end{tabular}
    \begin{itemize} \vspace{-5pt}
        \setlength{\itemsep}{-2pt}
        \item USB Logic Analyzer built around an STM32F446, capable of sniffing upto 500kHz signals.
        \item DMA data acquisition, and run-length encoded data transmission, to optimize byte usage on USB 2.0 FS.
        \item UART, SPI, I2C, and CAN signal decoding via a custom Go backend
        \item GUI with PyQt5 in Python
    \end{itemize}

    \raggedright\begin{tabular}{lr}
        \parbox[l]{3.65in}{{\bf{\large{BitSum Lecture Summarizer}}} \href{https://github.com/avr34/ECE381-Final}{(\underline{GitHub})}} &
        \parbox[r]{3.65in}{\raggedleft Oct 2025 - Dec 2025} \\
    \end{tabular}
    \begin{itemize} \vspace{-5pt}
        \setlength{\itemsep}{-2pt}
        \item Built a lecture summarizer tool, integrating Microsoft BitNet, OpenAI Whisper, and a custom feedforward network.
        \item Transcribes and summarizes lectures on CPU, 2x faster than human comprehension on average.
        \item Integrated with Docker to ensure reproducibility.
    \end{itemize}

    \raggedright\begin{tabular}{lr}
        \parbox[l]{3.65in}{{\bf{\large{NeuralNet}}} \href{https://github.com/avr34/NeuralNet}{(\underline{Github})}} &
        \parbox[r]{3.65in}{\raggedleft Oct 2024 - Feb 2025} \\
    \end{tabular}
    \begin{itemize} \vspace{-5pt}
        \setlength{\itemsep}{-2pt}
        \item Fully-Connected Neural Network Library for Regression and Classification in C.
        \item Backpropagation using Stochastic Gradient Descent in Matrix form.
        \item Last effort was converting to fixed-point weights, to run on resource constrained microcontrollers, TinyML style.
    \end{itemize}

\end{document}
